No time for dead time - Use the Fourier amplitude differences to normalize dead time-affected periodograms

### 2017-12-13 paper/deadtime.tex
New figure 1

\section{On the difference of Fourier amplitudes} \label{sec:fourierdiff}
\begin{figure*}
\gridline{\fig{rn_fourierdiff.eps}{0.33\textwidth}{(a)}
	\fig{wn_fourierdiff.eps}{0.33\textwidth}{(b)}
	\fig{fourier_vs_diff_dt.eps}{0.33\textwidth}{(c)}}

\caption{(a) and (b): Real-valued Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (a) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (b) no red noise and strong dead time, calculated over many 5\,s segments of the light curve. 
The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
The different behavior of Fourier amplitude differences under pure Poisson noise and dead time noise is evident, by comparing (a) and (b).
(c) Scatter distribution of the (averaged over multiple intervals) absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$. 
}
\label{fig:fourierdiff}
\end{figure*}

>>>>

\section{On the difference of Fourier amplitudes} \label{sec:fourierdiff}
\begin{figure*}
\plottwo{rn_fourierdiff}{wn_fourierdiff}
\caption{Real-valued Fourier amplitudes obtained by single light curves ($\mathcal{F}_1$) and difference between two realizations of the same source light curve ($\mathcal{F}_1 - \mathcal{F}_2$), plotted against each other in two cases: (Left) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (Right) no red noise and strong dead time, calculated over 5\,s segments of the light curve. 
The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
The different behavior of Fourier amplitude differences in the two cases is evident: in the deadtime-free case, the Fourier amplitude difference does \textit{not} correlate with the Fourier amplitude, while in the deadtime-affected case, this follows a precise linear relationship.
}
\label{fig:fourierdiff}
\end{figure*}
